---
title: "Final Porject Midpoint Deliverable"
author: "Amara, George, Lyons, Lufei Wang, Vicky"
date: "5/24/2019"
output: html_document
---

```{r setup, include = FALSE }
chooseCRANmirror(graphics=FALSE, ind=1)
knitr::opts_chunk$set(echo = TRUE)
source("scripts/barplot scripts.R")
source("scripts/Summary Information Script.R")
source("scripts/scatterplot script.R")
source("scripts/data table script.R")
source("scripts/linelot script.R")
library("knitr")
```


## Introduction of Problem Domain and Dataset
***
This is a report about **housing** in *King County*. We are interested in housing market becuase buying/renting a house is relative to **everyone**, especially in King County where housing prices are extremely high. We want to look at how the specifications of the house affect the housing price. This report draws upon data from the [House Sales in King County](https://www.kaggle.com/harlfoxem/housesalesprediction). This datasets contains the house sale prices for King County between May 2014 to May 2015. It includes 19 house features as well as the price and id columns. It is generated by Harlfoxem from *public record*.


## Summary Information On House Sold in King County
***
The *columns* of the dataset include `r get_summary_info(house_sales)$column_name`. One of the houses sold has `r get_summary_info(house_sales)$most_bedrooms` bedrooms which is the house that contain the **largest number of bedrooms**. Between May 2014 to May 2015 in King County, the **most expansive** house sold for $`r get_summary_info(house_sales)$most_expensive_room`, and the **cheapest house** sold for $`r get_summary_info(house_sales)$cheapest_room`. One house has a *total house square footage* of `r get_summary_info(house_sales)$largest_houst_ft` which is the **largerst house** sold. 


## Aggregate Table
***
Below is a table that summarizes information on average square footage, mean bedrooms, mean bathrooms and prices based on the **sizes** of the houses sold. The sizes are sorted by the **range of total square footages** with smaller square footages shown first.

```{r summary_state, echo = FALSE}
kable(get_chart(house_sales), col.names = c("Square Footage Range", "Average Square Footage", "Mean Number of Bedrooms","Mean Number of Bathrooms", "Mean Prices"))
```
We choose to include this table because we want to exam the relationship between the sizes of the houses and the prices they sold for. On average, the bigger the houses the more expand they are. One **outlier** we found is that the biggest houses(13,000-14,000) sold for a relavent lower price.

## Bar Chart for on 2B2B house.
***
Below is a bar chart that shows the relationship between price and floors on 2B2B houses.

```{r plot1, echo=FALSE} 
get_plot_info(house_sales)
```

Bar chart is a useful layout for comparing differences and making labels more legible. Although there are limitation, from the chart, we found that 2B2B houses that have **1.5** floors sold for the **highest** price and **2** floors sould for the **lowest** price.


## Scatterplot For Relationship of Price and Month Sold
Below is a scatterplot that shows the relationship of average prices sold and the month houses were sold.

```{r plot2, echo=FALSE} 
price_month_plot(house_sales)
```

Scatter plot is useful for showing how much one variable is affect by another. The relationship between the price and the month shows their correlation. From the plot, we found that selling price **peeked** on April and gradully goes down afterwards. The lowest average price is on Feb. 


## Plot 3
***
Below is a line graph that shows the relationship of average prices sold and the year that houses were sold.
```{r plot3, echo=FALSE} 
year_price_plot(house_sales)
```

Line graphs is useful for compaing changes over some period  of time. One thing we found **surprising** is that houses that were built around 1933 on average sold for the highest price. This could be an ourlier and is worth for future study. Houses that were **newer**(built after 2010) sold for relavent high prices as well, which was expected. 
