---
title: "Final Porject Midpoint Deliverable"
author: "Amara, George, Lyons, Lufei Wang, Vicky"
date: "5/24/2019"
output: html_document
---

```{r setup, include = FALSE }
chooseCRANmirror(graphics=FALSE, ind=1)
knitr::opts_chunk$set(echo = TRUE)
source("scripts/barplot scripts.R")
source("scripts/Summary Information Script.R")
source("scripts/scatterplot script.R")
library("knitr")
```

## Introduction of Problem Domain and Dataset
***
This is a report about **housing** in *King County*. We are interested in housing market becuase buying/renting a house is relative to **everyone**, especially in King County where housing prices are extremely high. We want to look at how the specifications of the house affect the housing price. This report draws upon data from the [House Sales in King County](https://www.kaggle.com/harlfoxem/housesalesprediction). This datasets contains the house sale prices for King County between May 2014 to May 2015. It includes 19 house features as well as the price and id columns. It is generated by Harlfoxem from *public record*.

## Summary Information On House Sold in King County
***
The *columns* of the dataset include `r get_summary_info(house_sales)$column_name`. One of the houses sold has `r get_summary_info(house_sales)$most_bedrooms` bedrooms which is the house that contain the **largest number of bedrooms**. Between May 2014 to May 2015 in King County, the **most expansive** house sold for $`r get_summary_info(house_sales)$most_expensive_room`, and the **cheapest house** sold for $`r get_summary_info(house_sales)$cheapest_room`. One house has a *total house suare footage* of `r get_summary_info(house_sales)$largest_houst_ft` which is the **largerst house** sold. 

## Aggregate Table
***



## Bar Chart for on 2B2B house.
***
Below is a bar chart that shows the relationship between price and floors on 2B2B houses.

```{r plot1, echo=FALSE} 
get_plot_info(house_sales)
```

Bar chart is a useful layout for comparing differences and making labels more legible. Although there are limitation, from the chart, we found that 2B2B houses that have **1.5** floors sold for the **highest** price and **2** floors sould for the **lowest** price.

## Scatterplot For Relationship of Price and Month Sold
Below is a scatterplot that shows the relationship of average prices sold and the month houses were sold.

```{r plot2, echo=FALSE} 
price_month_plot(house_sales)
```

Scatter plot is useful for showing how much one variable is affect by another. The relationship between the price and the month shows their correlation. From the plot, we found that selling price **peeked** on April and gradully goes down afterwards. The lowest average price is on Feb. 

## Plot 3
***
